State of the Practice for Lattice Boltzmann Method Software

### 2022-03-07 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed abstract and section 10 - recommendations

In this section we provide recommendations to address the pain points from
Section~\ref{painpoints} to answer~\rqref{RQ_Recommend}.  Our recommendations
are not lists of criticisms what should have been done in the past, or what
should be done now; they are just suggestions for consideration in the future.
We will not be repeating ideas here that have been discussed in previous
section, such as continuous integration, documentation of APIs, etc.  Our aim is
to mention ideas that are at least somewhat beyond conventional best practices.
The ideas listed have the potential to become best practices in the medium to
long-term.  The ideas are provided roughly in the order of increasing novelty.

@@

Linters can address the pain points for LBM developers.  For instance, a linter
can increase the amount of development time (\ppref{P_LackDevTime}) by
decreasing the number of mundane mistakes programmers have to catch.  Since the
linter can include rules that capture the wisdom of senior programmers, it can
help newer developers avoid common mistakes (\ppref{P_LackSoftDevExp}).  Although
there do not appear to be many linters for checking parallel programming
mistakes (\ppref{P_TechnologyHurdles}), Parallel Lint is an option for OpenMP.
If a linter is used consistently this can guard against some technical debt
(\ppref{P_TechDebt}). Although linters are thought of as tools for code
analysis, similar ideas can be applied to documentation to ensure that at least
the basic documentation rules are followed.  The use of tools to check
documentation is a partial explanation for the relatively higher quality of
statistical tools that are part of the Comprehensive R Archive Network (CRAN)
\citep{SmithEtAl2018_StatSoft}.

@@

Peer review is already a strategy adopted by some LBM developers to improve
confidence in their software (Section~\ref{SecReproducibility}), but the
benefits of peer review can be improved by making its application more rigorous.
\citet{Jones2008} shows that rigorous inspection finds 60-65\% of latent defects
on average, and often tops 85\% in defect removal efficiency.  By way of
comparison, most forms of testing average between 30 and 35\% for defect removal
efficiency \citep{EbertAndJones2009, Jones2008}.  A formal code inspection
involves asking the reviewer to either follow a review checklist (check
consistency of variable names, look for terminating loops, etc.), or perform
specific review tasks (like summarize the purpose of the code, create a data
dictionary for the module assigned, cross reference the code to the technical
manual, etc.) The task based inspection approach has been effectively used for
research software, as described by \citet{KellyAndShepard2000}. Task based
inspection is an ideal fit with an issue tracking system, like GitHub.  The
review tasks can be issues, so that they can be easily assigned, monitored and
recorded.  Other potential issues for the tracker include assigning junior team
members to test installation instructions and getting-started tutorials.

@@

\subsection{Augment Theory Manual to Include Requirements Information}

@@

Ensuring correctness was identified as a pain point by developers
(\ppref{P_Correctness}).  Inspired by \citet{BenureauAndRougier2017}, we make
recommendations to ensure that correctness can be maintained into the future by
prioritizing 4 increasingly sophisticated levels of replication.

>>>>

In this section we provide recommendations to address the pain points from
Section~\ref{painpoints} to answer~\rqref{RQ_Recommend}.  Our recommendations
are not lists of criticisms for what should have been done in the past, or what
should be done now; they are just suggestions for consideration in the future.
We will not be repeating ideas here that have been discussed in previous
sections, such as continuous integration, documentation of APIs, etc.  Our aim is to mention ideas that are at least somewhat beyond conventional best practices. The ideas listed here have the potential to become best practices in the medium to long-term. The ideas are presented roughly in the order of increasing novelty.

@@

Linters can address the pain points for LBM developers.  For instance, a linter
can decrease the amount of development time (\ppref{P_LackDevTime}) by
decreasing the number of mundane mistakes programmers have to catch.  Since the
linter can include rules that capture the wisdom of senior programmers, it can
help newer developers avoid common mistakes (\ppref{P_LackSoftDevExp}).  Although
there do not appear to be many linters for checking parallel programming
mistakes (\ppref{P_TechnologyHurdles}), Parallel Lint is an option for OpenMP.
If a linter is used consistently this can guard against some technical debt
(\ppref{P_TechDebt}). Although linters are thought of as tools for code
analysis, similar ideas can be applied to documentation to ensure that at least
the basic documentation rules are followed.  The use of tools to check
documentation is a partial explanation for the relatively higher quality of
statistical tools that are part of the Comprehensive R Archive Network (CRAN)
\citep{SmithEtAl2018_StatSoft}.

@@

Peer review is a strategy already adopted by some LBM developers to improve
confidence in their software (Section~\ref{SecReproducibility}), but the
benefits of peer review can be improved by making its application more rigorous.
\citet{Jones2008} shows that rigorous inspection finds 60-65\% of latent defects
on average, and often tops 85\% in defect removal efficiency.  By way of
comparison, most forms of testing average between 30 and 35\% for defect removal
efficiency \citep{EbertAndJones2009, Jones2008}.  A formal code inspection
involves asking the reviewer to either follow a review checklist (check
consistency of variable names, look for terminating loops, etc.), or perform
specific review tasks (like summarize the purpose of the code, create a data
dictionary for the module assigned, cross reference the code to the technical
manual, etc.) The task based inspection approach has been effectively used for
research software, as described by \citet{KellyAndShepard2000}. Task based
inspection is an ideal fit with an issue tracking system, like GitHub.  The
review tasks can be issues, so that they can be easily assigned, monitored and
recorded.  Other potential issues for the tracker include assigning junior team
members to test installation instructions and getting-started tutorials.

@@

\subsection{Augment Theory Manuals to Include Requirements Information}

@@

Ensuring correctness was identified as a pain point by developers
(\ppref{P_Correctness}).  Inspired by \citet{BenureauAndRougier2017}, we make
recommendations to ensure that correctness can be maintained into the future by
prioritizing four increasingly sophisticated levels of replication.
